Figure 6 - networks

### 2024-08-05 ms_figure_6_networks.Rmd
Reorder panels Fig6

```{r}
md <- metadata(sce500)
volc <- md$testres$tests$Pho7_500_plate_vs_compl_Pho7_500_plate |>
    mutate(signif = adj.P.Val < adjpThreshold & logFC > log2fcThreshold)
(pho7volc <- ggplot(volc, aes(x = logFC, y = mlog10p)) + 
        geom_text_repel(data = volc |> filter(signif),
                        aes(label = pid), min.segment.length = 0,
                        max.overlaps = Inf) + 
        geom_point(aes(alpha = signif, color = signif), 
                   show.legend = c(alpha = FALSE, color = TRUE)) + 
        scale_color_manual(values = c(`TRUE` = main_colors[5], `FALSE` = na_color), 
                           labels = c(`TRUE` = paste0("adj. p < ", adjpThreshold, 
                                                      " and logFC > ", log2fcThreshold)),
                           na.value = "black", breaks = "TRUE") + 
        scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.5)) + 
        geom_point(data = volc |> dplyr::filter(pid == "Pho7") |>
                       dplyr::mutate(type = "Bait"), 
                   mapping = aes(fill = type), color = main_colors[3], 
                   shape = 21, alpha = 1, size = 2) + 
        scale_fill_manual(values = c(Bait = main_colors[3])) + 
        labs(x = "log2(fold-change)", y = "-log10(p-value)", 
             title = "Pho7 vs complement (500 mM NaCl)") + 
        theme_cowplot(ft) + 
        theme(legend.position = "bottom") + 
        guides(color = guide_legend(nrow = 1, byrow = TRUE, title = ""),
               fill = guide_legend(nrow = 1, byrow = TRUE, title = "")))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(
            cowplot::plot_grid(NULL, fig6c, NULL, nrow = 1,
                               rel_widths = c(0.25, 1, 0.1)),  
            ggrad_upset,
            ncol = 1, labels = c("C", "D"),
            rel_heights = c(1, 1.75)), 
        pho7volc, 
        nrow = 1, labels = c("", "E")
    ),
    rel_heights = c(5, 3.5), 
    ncol = 1
)
```

>>>>

```{r}
md <- metadata(sce500)
volc <- md$testres$tests$Pho7_500_plate_vs_compl_Pho7_500_plate |>
    mutate(signif = adj.P.Val < adjpThreshold & logFC > log2fcThreshold)
(pho7volc <- ggplot(volc, aes(x = logFC, y = mlog10p)) + 
        geom_text_repel(data = volc |> filter(signif),
                        aes(label = pid), min.segment.length = 0,
                        max.overlaps = Inf) + 
        geom_point(aes(alpha = signif, color = signif), 
                   show.legend = c(alpha = FALSE, color = TRUE)) + 
        scale_color_manual(values = c(`TRUE` = main_colors[5], `FALSE` = na_color), 
                           labels = c(`TRUE` = paste0("adj. p < ", adjpThreshold, 
                                                      " and logFC > ", log2fcThreshold)),
                           na.value = "black", breaks = "TRUE") + 
        scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.5)) + 
        geom_point(data = volc |> dplyr::filter(pid == "Pho7") |>
                       dplyr::mutate(type = "Bait"), 
                   mapping = aes(fill = type), color = main_colors[3], 
                   shape = 21, alpha = 1, size = 2) + 
        scale_fill_manual(values = c(Bait = main_colors[3])) + 
        labs(x = "log2(fold-change)", y = "-log10(p-value)", 
             title = "Pho7 vs complement (500 mM NaCl IP-MS)") + 
        theme_cowplot(ft) + 
        theme(legend.position = "bottom") + 
        guides(color = guide_legend(nrow = 1, byrow = TRUE, title = ""),
               fill = guide_legend(nrow = 1, byrow = TRUE, title = "")))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        pho7volc, 
        cowplot::plot_grid(
            cowplot::plot_grid(NULL, fig6c, NULL, nrow = 1,
                               rel_widths = c(0.25, 1, 0.1)),  
            ggrad_upset,
            ncol = 1, labels = c("B", "C"),
            rel_heights = c(1, 1.75)), 
        nrow = 1, labels = c("A", "")
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none") + 
                ggtitle("150 mM NaCl IP-MS") + 
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            ggr500 + theme(legend.position = "none") + 
                ggtitle("500 mM NaCl IP-MS") +
                theme(plot.title = element_text(hjust = 0.075, size = ft)), 
            nrow = 1, labels = c("D", "E")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    rel_heights = c(3.5, 5), 
    ncol = 1
)
```
